\begin{literatura}{99}
	
\bibitem{osta-udf-0260}
    \emph{Universal Disk Format Specification}. Revision 2.60. Santa Clara, California: Optical Storage Technology Association, 2005.

\bibitem{osta-udf-0201}
    \emph{Universal Disk Format Specification}. Revision 2.01. Cupertino, California: Optical Storage Technology Association, 2000.

\bibitem{osta-udf-0150}
    \emph{Universal Disk Format Specification}. Revision 1.50. Santa Barbara, California: Optical Storage Technology Association, 1997.

\bibitem{ecma-167}
    \emph{ECMA-167}. 3rd Edition. Geneva, Switzerland: [online] ECMA, 1997 [cit. 2016-10-18]. Dostupné z: \url{https://www.ecma-international.org/publications/files/ECMA-ST/Ecma-167.pdf}

\bibitem{ecma-168}
    \emph{ECMA-168}. 2nd Edition. Geneva, Switzerland: [online] ECMA, 1994 [cit. 2017-05-07]. Dostupné z: \url{https://www.ecma-international.org/publications/files/ECMA-ST/Ecma-168.pdf}

\bibitem{udffsck-git}
    \emph{Fsck tools for UDF. In: GitHub}\/ [online]. 2016 [cit. 2016-09-30]. Dostupné z: \url{https://github.com/JElchison/format-udf/wiki/fsck-tools-for-UDF}

\bibitem{wayback}
    \emph{Internet Archive}\/ [online]. 2007 [cit. 2016-11-21]. Dostupné z: \url{http://web.archive.org/web/20070702054203/http://www.hitech-projects.com/udf/download/}

\bibitem{udftools-sourceforge}
    \emph{Linux UDF. In: Sourceforge}\/ [online]. 2004 [cit. 2016-11-21]. Dostupné z: \url{https://sourceforge.net/projects/linux-udf/}

\bibitem{udftools-github}
    \emph{pali/udftools. In: GitHub}\/ [online]. 2016 [cit. 2016-11-21]. Dostupné z: \url{https://github.com/pali/udftools}

\bibitem{scottuvblog}
    \emph{UDF Filesystem}\/ [online]. 2002 [cit. 2016-11-21]. Dostupné z: \url{https://people.freebsd.org/~scottl/}

\bibitem{13monkey}
    \emph{13thmonkey.org: udfclient}\/ [online]. 2016 [cit. 2016-11-21]. Dostupné z: \url{www.13thmonkey.org/udfclient}  

\bibitem{solaris-github}
    \emph{illumos/illumos-gate. In: GitHub}\/ [online]. 2016 [cit. 2016-11-21]. Dostupné z: \url{https://github.com/illumos/illumos-gate/tree/f7877f5d39900cfd8b20dd673e5ccc1ef7cc7447/usr/src/cmd/fs.d/udfs/fsck} 

\bibitem{posix-mmap}
    Mmap. \emph{The Single UNIX ® Specification, Version 2} [online]. The Open Group, 1997 [cit. 2017-01-02]. Dostupné z: \url{http://pubs.opengroup.org/onlinepubs/7908799/xsh/mmap.html}

\bibitem{arch-lvm}
    Software RAID and LVM. \emph{ArchWiki} [online]. ArchLinux, 2016 [cit. 2017-01-02]. Dostupné z: \url{https://wiki.archlinux.org/index.php/Software_RAID_and_LVM}

\bibitem{tldp-filesystem}
    Filesystems. \emph{The Linux Documentation Project} [online]. [cit. 2017-01-02]. Dostupné z: \url{http://www.tldp.org/LDP/sag/html/filesystems.html}

\bibitem{nongnu-ext2}
    The Second Extended File System. \emph{Nongnu.org} [online]. 2011 [cit. 2017-01-02]. Dostupné z: \url{http://www.nongnu.org/ext2-doc/ext2.html}

\bibitem{linmag-ext}
    The ext filesystem – a four-generation retrospective. \emph{Linux Magazine} [online]. Linux New Media, 2013 [cit. 2017-01-02]. Dostupné z: \url{http://www.linux-magazine.com/Issues/2013/156/The-ext-Filesystem}

\bibitem{paper-ext3}
    BADARI, Pulavarty, Mingming CAO, Theodore PULAVARTY a Suparna BHATTACHARYA. \emph{State of the Art: Where we are with the Ext3 filesystem} [online]. 2005 [cit. 2017-01-02]. Dostupné z: \url{http://ext2.sourceforge.net/2005-ols/paper-html/}

\bibitem{paper-ext4}
    CAO, Mingming, Suparna BHATTACHARYA a Ted TSO. \emph{Ext4: The Next Generation of  Ext2/3 Filesystem} [online]. 2007, , 36 [cit. 2017-01-02]. Dostupné z: \url{https://www.usenix.org/legacy/event/lsf07/tech/cao_m.pdf}

\bibitem{man-fsck}
    Fsck. \emph{Die.net} [online]. [cit. 2017-01-02]. Dostupné z: \url{https://linux.die.net/man/8/fsck}
\bibitem{man-open}
    Open. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/open}
\bibitem{man-fopen}
    Fopen. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/3/fopen}
\bibitem{man-flock}
    Flock. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/flock}
\bibitem{man-mmap}
    Mmap. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/mmap}
\bibitem{man-fstat}
    Fstat. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/fstat}
\bibitem{man-fseeko}
    Fseeko. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/3/fseeko}
\bibitem{man-ftello}
    Ftello. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/3/ftello}
\bibitem{man-fseek}
    Fseek. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/3/fseek}
\bibitem{man-ftell}
    Ftell. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/3/ftell}
\bibitem{man-read}
    Read. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/read}
\bibitem{man-write}
    Write. \emph{Die.net} [online]. [cit. 2017-05-07]. Dostupné z: \url{https://linux.die.net/man/2/write}

\bibitem{man-isovfy}
    Isoinfo. \emph{Die.net} [online]. [cit. 2017-01-02]. Dostupné z: \url{https://linux.die.net/man/8/isoinfo}

\bibitem{paragon-ntfs}
    NTFS for Mac 14. \emph{Parargon Software Group} [online]. 2017 [cit. 2017-05-07]. Dostupné z: \url{https://www.paragon-software.com/cz/home/ntfs-mac/}

\bibitem{dcn}
    UDF 2.60 - All approved DCNs. \emph{Internet Archive}\/ [online]. 2007 [cit. 2017-05-07]. Dostupné z: \url{https://web.archive.org/web/20161119014819/http://www.osta.org/specs/pdf/udf260_allApprovedDCNs.pdf}

\bibitem{crc-prednasky}
    Datová komunikace. \emph{UTKO} [online]. 2010 [cit. 2017-05-07]. Dostupné z: \url{http://anca.utko.feec.vutbr.cz/vyuka/bdak}


\end{literatura}

